Centralizers of higher enveloping algebras of Lie algebras

### 2020-09-03 draft.tex
comments twd future

\brian{HKR}

Consider the case $n=1$ and $B = U \fg$ where $f$ is simply the identity map. 
A classic result of \cite{HochSerre} is that the Hochschild cohomology of $U \fg$ can be expressed in terms of Lie algebra cohomology as $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg^{ad})$. 
On the right-hand side, we take the Chevalley--Eilenberg cochain complex with values in the module $U \fg$ equipped with the adjoint action.
The algebra structure is given by a special case of the convolution product as in Section \ref{??}.

On the other hand, our model for the derived center ${\frak Z}(U(\fg))$ of $U \fg$ is the one-dimensional factorization algebra assigning the cochain complex
\[
\clies(\fg \otimes \Omega^*(U), \cliels( \fg \otimes \Omega^*_c(U)))
\]
to each open set $U \subset \RR$.
In the case that $U$ is an interval, this cochain complex is quasi-isomorphic to $\clies (\fg , U\fg^{ad})$.
Furthermore, one can verify that the resulting $E_1$-algebra structure agrees with the one coming from convolution.

Our model also gives us a simple description of the factorization homology of the derived center along the circle $S^1$.
\[
\int_{S^1} {\frak Z}(U(\fg)) \simeq \clies(\fg[\epsilon], \cliels( \fg[\epsilon])),
\]
where $\epsilon$ is a formal variable of degree~$1$. 
\brian{We should compare with Tamarkin-Tsygan's noncommutative calculus (cf. section 2.6).
We could exhibit Theorem 2.7.1 explicitly in this case for the $E_n$ case with enveloping algebras.}

@@

@@

@@

\section{Examples}

>>>>

%
%\brian{HKR}
%
%Consider the case $n=1$ and $B = U \fg$ where $f$ is simply the identity map. 
%A classic result of \cite{HochSerre} is that the Hochschild cohomology of $U \fg$ can be expressed in terms of Lie algebra cohomology as $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg^{ad})$. 
%On the right-hand side, we take the Chevalley--Eilenberg cochain complex with values in the module $U \fg$ equipped with the adjoint action.
%The algebra structure is given by a special case of the convolution product as in Section \ref{??}. 
%
%On the other hand, our model for the derived center ${\frak Z}(U(\fg))$ of $U \fg$ is the one-dimensional factorization algebra assigning the cochain complex
%\[
%\clies(\fg \otimes \Omega^*(U), \cliels( \fg \otimes \Omega^*_c(U)))
%\]
%to each open set $U \subset \RR$.
%In the case that $U$ is an interval, this cochain complex is quasi-isomorphic to $\clies (\fg , U\fg^{ad})$.
%Furthermore, one can verify that the resulting $E_1$-algebra structure agrees with the one coming from convolution. 
%
%Our model also gives us a simple description of the factorization homology of the derived center along the circle $S^1$.
%\[
%\int_{S^1} {\frak Z}(U(\fg)) \simeq \clies(\fg[\epsilon], \cliels( \fg[\epsilon])),
%\]
%where $\epsilon$ is a formal variable of degree~$1$. 
%\brian{We should compare with Tamarkin-Tsygan's noncommutative calculus (cf. section 2.6).
%We could exhibit Theorem 2.7.1 explicitly in this case for the $E_n$ case with enveloping algebras.}

@@

\subsection{How factorization homology intertwines with taking the center}

\owen{Explain why there is a canonical map from the fact hlgy of a center to the center of the fact hlgy}

\begin{prp}
For any $L_\infty$ algebra $\fg$ and any closed $(n-k)$-dimensional manifold $S$,
the canonical map of $E_k$-algebras
\[
\int_{S} \fZ_n(\fg) \to \fZ_k \left( \int_S \UU_n \fg \right)
\]
is a weak equivalence.
\end{prp}

As a slogan, we say ``factorization homology commutes with taking centers,'' 
at least for enveloping $E_n$ algebras.
It is natural to ask whether this result holds in general.

\begin{qtn}
Is the canonical map always a weak equivalence?
\end{qtn}

\owen{We should see if that's what Tamarkin-Tsygan prove for  $E_1$ algebras, as it would be further evidence.}

\owen{Then ask what is the factorization homology on a compact manifold with boundary, which leads into next section.}

@@

\owen{Somewhere please mention that the slogan ``quantization commutes with pushforward'' holds for this class of theories.}

@@

\section{Examples?}
